Software Citation Principles

### 2016-07-20 sc-principles/software-citation-principles.tex
added mention of new appendix

The group gathered members (see Appendix~\ref{app:wg_members}) in April and May 2015,
and then began work in June, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and subsequently draft this resulting document,
which was presented and discussed at the Force2016 Conference~\cite{force2016}
in April 2016.  This discussion led to a second, final version, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the research process.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Feedback following FORCE16}
\label{app:force16-feedback}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The group gathered members (see Appendix~\ref{app:wg_members}) in April and May 2015,
and then began work in June, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and subsequently draft an initial version of this document.
The draft Software Citation Principles document was discussed in a day-long workshop and presented at the FORCE2016 Conference~\cite{force2016} in April 2016.
Members of the workshop and greater FORCE11 community gave feedback, which we recorded here in Appendix~\ref{app:force16-feedback}.
This discussion led to a second, final version.
We also plan to initiate a follow-on working group that will work with stakeholders to ensure that these principles impact the research process.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Feedback following FORCE2016}
\label{app:force16-feedback}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
